---
title: "Day4"
format: html
editor: visual
execute: 
  warning: false
---

## Functions

Make a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}

double_value(my_dollars = 10.13)
# OR, because it is expecting 1 value and you are entering 1 value you do not need to specify
double_value(10.13)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)
# works on a vector
double_value(monthly_income)
```

```{r}

double_value2 <- function(dollars) {
  dollars * 2
}

double_value2(dollars = 10)
```

Print statement = "show me"

return statement = "store me"

Create a function that returns a restaurant name given a cool animal and your favorite food

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given a temperature in degrees fahrenheit, write a function that converts it to celcius

```{r}
convert_fc <- function(temp_f) {
  print((temp_f - 32) * (5/9))
}

```

```{r}

convert_fc(temp_f = 52)
```

Create a function that given inputs of age and hometown returns "I am \_ years old, and Im from \_"

```{r}
describe_person <- function(age_yr, home_town) {
  print(paste("I am", age, "years old, and I'm from", home_town))
}

describe_person(age = 20, home_town = "Pleasanton")
```
